Intercoder ICBEdataset_figure_semantic_embeddings

### 2022-01-26 README.Rmd
input datas

## ICBe raw data

 - Agreed Data, long form (LINK NEEDED)
 - Agreed Data, wide form (LINK NEEDED)
 - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
    + values may contain multiple entries separating with a semicolon
 - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
    + each row contains identifying information for a coder-crisis-event-sentence
    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
    + each value contains a single entry
 - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.

## Other data inputs:

### ICBe prep
- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
  + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
- [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)

### Existing datasets
- [The ICB project](https://sites.duke.edu/icbdata/) system-level (./data/icb1v14.Rds) and actor-level (./data/icb2v14.Rds) datasets.
- [ICEWS data sample](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/28075/WNOBVV&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData).

>>>>

## ICBe data products

 - Agreed Data, long form (LINK NEEDED)
 - Agreed Data, wide form (LINK NEEDED)
 - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.

### Additional data versions
 - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
    + values may contain multiple entries separating with a semicolon
 - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
    + each row contains identifying information for a coder-crisis-event-sentence
    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
    + each value contains a single entry

## Data inputs:

### ICBe preperation
  - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
    + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
  - [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)

### External datasets
  - [The ICB project](https://sites.duke.edu/icbdata/) 
    + System-level (./data/icb1v14.Rds) and Actor-level (./data/icb2v14.Rds) datasets
    + Dyadic-Level Crisis Data ([source](https://sites.duke.edu/icbdata/data-collections/))
  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI 5.01) and incident-participant level (MIDIP 5.01) converted to Rds. 
  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global)
  - cameo.eventcode.txt adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf)
  - [Phoenix Event data](https://databank.illinois.edu/datasets/IDB-2796521)
  - [Terrier event data](https://osf.io/4m2u7/files/) 
    + too large to include in the github repository
    + to replicate, download the folder 'largegeolocatedata' to ICBEdata/replication_paper/data/ignore and decompress
  - [ICEWS data sample](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData)
    + too large to include in the github repository
    + to replicate, download the .tsv and .tab files to ICBEdata/replication_paper/data/ignore/icews_dataverse/ and decompress

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
input datas

```{r message=FALSE}
target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
# in not working, run googledrive::drive_auth() and select new token

>>>>

```{r message=FALSE}
target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
# in not working, run googledrive::drive_auth() and select new token

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
input datas

midip <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.csv'))

midii <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.csv'))

@@

icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")

@@

CAMEO_eventcodes <- read_tsv(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
dim(icews)

@@

dim(icews) #15,751,586
icews_clean <- icews %>% 
               left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode) %>%  #You have 
                           dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  )  %>%
                filter(source_country %in% na.omit(actor_translator$ICEWS_Country) | source_name %in% na.omit(actor_translator$ICEWS_Actor.Name)) %>%
                filter(target_country %in% na.omit(actor_translator$ICEWS_Country) | target_name %in% na.omit(actor_translator$ICEWS_Actor.Name) ) %>%
                filter(!source_sectors %>% str_detect(kill_sectors_regex)) %>%
                filter(!target_sectors %>% str_detect(kill_sectors_regex)) %>%
                #Just apply the wikidata actor labels
                #mutate(source=ifelse(is.na(source_country) , source_name, source_country)) %>%
                #mutate(target=ifelse(is.na(target_country) ,target_name , target_country)) %>%
                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% distinct() %>% na.omit() ) %>%
                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%

@@

a <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
b  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
c  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
d  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
e <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

>>>>

midii <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.Rds'))
midip <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.Rds'))

@@

#icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
icbdy_20 <- readRDS(paste0(here::here(), '/replication_paper/data/in/icbdy_20.Rds'))

@@

CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/"), full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()

dim(icews)

@@

dim(icews) #15,751,586
icews_clean <- icews %>% 
               left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code) # %>%  #You have 
                           # dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  
                         )  %>%
                filter(source_country %in% na.omit(actor_translator$ICEWS_Country) | source_name %in% na.omit(actor_translator$ICEWS_Actor.Name)) %>%
                filter(target_country %in% na.omit(actor_translator$ICEWS_Country) | target_name %in% na.omit(actor_translator$ICEWS_Actor.Name) ) %>%
                filter(!source_sectors %>% str_detect(kill_sectors_regex)) %>%
                filter(!target_sectors %>% str_detect(kill_sectors_regex)) %>%
                #Just apply the wikidata actor labels
                #mutate(source=ifelse(is.na(source_country) , source_name, source_country)) %>%
                #mutate(target=ifelse(is.na(target_country) ,target_name , target_country)) %>%
                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% distinct() %>% na.omit() ) %>%
                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%

@@

a <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-NYT_1980-2018.Rds'))
b <- dplyr::bind_rows(
  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019a.Rds')),
  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019b.Rds')),          
  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019c.Rds')))
c <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixFBIS_1995-2004.Rds'))
d <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixNYT_1945-2005.Rds'))
e <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixWSJ_1945-2006.Rds'))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
input datas

codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
codings_long <- readRDS(file=paste0(here::here(), '/data_out/codings_long.Rds'))
codings_long_agreement <- readRDS(file=paste0(here::here(), '/data_out/codings_long_agreement.Rds'))

@@

```{r, messages=F, results='hide'}
library(reticulate)
#py_discover_config()
use_python("/home/skynet3/anaconda3/bin/python/")

@@

codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)

codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_long_agreed_embeded.Rds'))

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_data/out/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)

@@

codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_wide_agreed_embeded.Rds'))

@@

p_semantic_embeddings   %>% saveRDS(paste0(here::here(), '/paper_replication/figures/p_semantic_embeddings.Rds'))
p_semantic_embeddings

>>>>

codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))

@@

```{r, messages=F, results='hide'}
library(reticulate)
#py_discover_config()

use_python("/home/skynet3/anaconda3/bin/python/")

@@

codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)

codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_long_agreed_embeded.Rds'))

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)

@@

codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_wide_agreed_embeded.Rds'))

@@

p_semantic_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
p_semantic_embeddings
